The evolution of the transcriptome of mammalian placentas

### 2016-11-12 manuscript/manuscript.Rnw
discuss placenta attachment shape

Supplemental \cref{tab:shape_genes} shows the top 50 genes which are
associated with the shape of placenta attachment, as well as the shape
in which the difference is most significant.

\textit{EREG} -- ligand of EGFR, known to be expressed in some
placentas but apparently not present in the term placentas of \human.

\textit{UNC} -- totally unknown

>>>>

Supplemental \cref{tab:shape_genes} shows the top 50 genes which are
associated with the shape of placenta attachment, as well as the shape
in which the difference is most significant. The most significant
genes which were associated with diffuse placenta attachment include
\textit{EREG}, a ligand of EGFR, \textit{UNC93A}, a homolog of
\textit{UNC93B1} which is involved in the balancing between Tlr7 and
Tlr9 immune response in mice\DLA{cite TLR7/TLR9 paper}, and
\textit{WNT5A}, which inhibits the invasion of the trophoblast cell
line HTR8/SVneo \textit{in vitro} \DLA{Cite this paper after reading
  the comments on it (PMID: 26865089)}.
